An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-18 Article/EconGrowth2-GraphsOnly.Rnw
Moved all loading first.

# Load coefficients from all models in one large data frame
# coeffs_df <- tbl_df( readRDS("../AllCoef.rda") )
coeffs_df <- tbl_df(AllCoef)
# Rearrange the country factors to obtain our preferred ordering.
coeffs_df$country <- as.factor(coeffs_df$country)
for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
# Change the names of the energy factors to the names for the graph
coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
# Rearrange the energy factors to obtain our preferred ordering.
coeffs_df$energy <- as.factor(coeffs_df$energy)
energyLevels <- c(none="none", q="q", x="x", u="u")
for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }

# Load fitted data from all models in one large data frame
# fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
fitted_df <- tbl_df(AllFitted)
# Rearrange the energy factors to obtain our preferred ordering.
fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
fitted_df$energy <- as.factor(fitted_df$energy)
for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }

>>>>

# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(AllCoef)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(AllFitted)

# Rearrange the country factors to obtain our preferred ordering.
coeffs_df$country <- as.factor(coeffs_df$country)
for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
# Change the names of the energy factors to the names for the graph
coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
# Rearrange the energy factors to obtain our preferred ordering.
coeffs_df$energy <- as.factor(coeffs_df$energy)
energyLevels <- c(none="none", q="q", x="x", u="u")
for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }

# Rearrange the energy factors to obtain our preferred ordering.
fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
fitted_df$energy <- as.factor(fitted_df$energy)
for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
